Temporality is Important for Networks of Hospital Patient Transfers

### 2024-10-30 reports/report.qmd
support coloneqq

---
title: "Temporality is Important for Networks of Hospital Patient Transfers"
authors:
    - name: David Wu
    - name: Michael Lydeamore
    - name: Andrew Stewardson
    - name: Tjibbe Donker
    - name: Nic Geard
    - name: "******"
date: last-modified
format:
    html: default
    pdf: default
bibliography: refs.bib
csl: plos.csl
jupyter: python3
filters:
    - diagram
execute:
    echo: false
    warning: false
    error: false
---

@@

A network or graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ is made up of nodes or vertices $\mathcal{V} = \{v_1, v_2, \dots\}$ and edges $\mathcal{E} = \{e_{ij} \coloneqq (v_i, v_j), \dots\}$ that join those nodes. Each edge $e_{ij}$ can be assigned attributes, including an edge weight $w_{ij}$.
For our application, this edge weight will typically represent the number of observed movements in a given time period. Thus the network can encode a representation of the movement between hospitals over a given time period.

@@

sns.histplot(
    combined_all_df, 
    x = 'extent', 
    hue = 'simulation', 
    multiple = 'dodge', 
    bins = extent_bins, 
    shrink = 0.8, 
    hue_order = sim_type_order,
    discrete = True,
)
sns.despine()
```

>>>>

---
title: "Temporality is Important for Networks of Hospital Patient Transfers"
authors:
    - name: David Wu
    - name: Michael Lydeamore
    - name: Andrew Stewardson
    - name: Tjibbe Donker
    - name: Nic Geard
    - name: "******"
date: last-modified
format:
    html: default
    pdf:
        include-in-header:
            - text: |
                \usepackage{mathtools}
        papersize: a4
bibliography: refs.bib
csl: plos.csl
jupyter: python3
filters:
    - diagram
execute:
    echo: false
    warning: false
    error: false
---

@@

A network or graph $\mathcal{G} = (\mathcal{V}, \mathcal{E})$ is made up of nodes or vertices $\mathcal{V} = \{v_1, v_2, \dots\}$ and edges $\mathcal{E} = \{e_{ij} \coloneqq (v_i, v_j)\}$ that join those nodes. Each edge $e_{ij}$ can be assigned attributes, including an edge weight $w_{ij}$.
For our application, this edge weight will typically represent the number of observed movements in a given time period. Thus the network can encode a representation of the movement between hospitals over a given time period.

@@

sns.histplot(
    combined_all_df, 
    x = 'extent', 
    hue = 'simulation', 
    multiple = 'dodge', 
    bins = extent_bins, 
    hue_order = sim_type_order,
    discrete = True,
)
sns.despine()
```
